Practical Challenges with Web Service Evolution:\\A Review of Literature and Current Industry Practices

### 2013-06-05 paper.tex
added the  counts to each section

From the search results, we performed a primary screening and selected 21 papers after reading the abstracts. Then, for the remaining articles, we read the full paper as long as it was found relevant, i.e. only if it contained topics about the evolution of web services. The resulting list is composed of \cite{kitchenham2007guidelines} \cite{petersen2008systematic} \cite{treiber2009analyzing} \cite{borovskiy2008evolution} \cite{lublinsky2007versioning} \cite{laskey2008considerations} \cite{wilde2004semantically} \cite{leitner2008end} \cite{mangler2010origin} \cite{kaminski2006design} \cite{le2008synchronizing} \cite{aversano2005visualizing}.

@@

\subsubsection{Why Do Web Services Evolve?} % (fold)
\label{sub:why_do_web_services_change}
In this section, we have discussed the drivers behind web service evolution from the related literature. To begin with, in \cite{treiber2009analyzing} Treiber et al. provided a list of changes related to web services with their interdependencies. To identify the source and impact of a change, they categorized the stakeholders into four roles:

@@

\subsubsection{How to evolve the web services?} % (fold)
\label{sub:how_to_evolve_the_web_services_}
Now that we have listed the drivers behind web service evolution, next we present the different approaches to tackle web service evolution based on the existing literature.

@@

Using a similar approach but instead of arbitrary custom tags to extend the schema, Fang et al. provides a concrete list of six XML nodes to create a version-aware service model for SOAP web services [A Version-aware Approach for Web Service Directory]. They introduced extensions to WSDL and UDDI to tackle evolving web services. These extensions are composed of six XML nodes: \textbf{1) version name, 2 ) version description, 3) startTime of the version, 4) endTime of the version, 5) alias such as (new, current etc) of the version name and, 6) original version that preceded it}.

@@

\subsubsection{Communication:}
A change in a web service may impact multiple stakeholders. So, it is important to communicate the changes and their impacts to the stakeholders as the service evolves. In this section, we have discussed the suggested ways to effectively communicate about the changes from the existing literature.

>>>>

From the search results, we performed a primary screening and selected 21 papers after reading the abstracts. Then, for the remaining articles, we read the full paper as long as it was found relevant, i.e. only if it contained topics about the evolution of web services. The resulting list is composed of \cite{kitchenham2007guidelines} \cite{petersen2008systematic} \cite{treiber2009analyzing} \cite{borovskiy2008evolution} \cite{lublinsky2007versioning} \cite{laskey2008considerations} \cite{wilde2004semantically} \cite{fang2007version} \cite{leitner2008end} \cite{mangler2010origin} \cite{kaminski2006design} \cite{le2008synchronizing} \cite{aversano2005visualizing}.

@@

\subsubsection{Why Do Web Services Evolve?} % (fold)
\label{sub:why_do_web_services_change}
In this section, we have listed the drivers behind web service evolution as discussed in 3 of the selected papers. To begin with, in \cite{treiber2009analyzing} Treiber et al. provided a list of changes related to web services with their interdependencies. To identify the source and impact of a change, they categorized the stakeholders into four roles:

@@

\subsubsection{How to evolve the web services?} % (fold)
\label{sub:how_to_evolve_the_web_services_}
Now that we have listed the drivers behind web service evolution, next we present the different approaches to tackle web service evolution based on 6 of the selected papers.

@@

Using a similar approach but instead of arbitrary custom tags to extend the schema, Fang et al. provides a concrete list of six XML nodes to create a version-aware service model for SOAP web services \cite{fang2007version}. They introduced extensions to WSDL and UDDI to tackle evolving web services. These extensions are composed of six XML nodes: \textbf{1) version name, 2 ) version description, 3) startTime of the version, 4) endTime of the version, 5) alias such as (new, current etc) of the version name and, 6) original version that preceded it}.

@@

\subsubsection{Communication:}
A change in a web service may impact multiple stakeholders. So, it is important to communicate the changes and their impacts to the stakeholders as the service evolves. In this section, we have discussed 2 of the selected papers as they suggested ways to effectively communicate the evolution of web services.
